---
title: "CytofIN testing"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 
```{r}
library(devtools)
library(usethis)
library(tidyverse)
```


# Installation

```{r}
install_github("bennyyclo/Cytofin")

```

Comments: Installation takes a while - way longer than I would expect. I think this is because you include a decent amount of data inside the package in the form of .fcs files (in `Cytofin/inst/extdata`). 

# Loading

```{r}
library(cytofin)
```


# Documentation 

Most R packages are documented not only on the function level, but also on the whole-package level. 

```{r}
help(package = "cytofin")
```

From running this command, we can see that your `DESCRIPTION` file (which should be at the root of your R package directory on your local machine) doesn't have the **Title** field filled in. I recommend filling it in with *Homogenize and Integrate Heterogeneous Mass Cytometry Data From Multiple Data Sets*.

We can also see that there are 4 functions in this R package: 

* `annorm()`: Normalize CyTOF data panel
* `annorm_nrs()`: Normalize CyTOF data panel
* `anprep()`: Prep CyTOF control for normalization
* `homogenize()`: Homogenize CyTOF data panel


```{r}

```


# Functions

#










